Harmful Anti-Foreign Sentiments based on Concern for Competition Should be Recognized and Addressed

### 2023-02-21 outputs/paper/paper.qmd

In Canada, hate crimes based on race and ethnicity increased by 80% in 2020, with the highest number of incidents targeting black individuals, followed by east and southeast Asians, indigenous individuals, and the lowest number of victims being South Asian individuals [@moreau_wang_2022]. Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 and 130,125 refugees in 2020, these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents [@government_of_canada_2022].

@@

We will first discuss \_\_\_\_\_\_\_\_INSERT FORMT HERE\_\_\_\_\_\_\_\_\_\_

@@

(1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats

(2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians

@@

## Future Research

>>>>

In Canada, hate crimes based on race and ethnicity increased by 80% in 2020, with the highest number of incidents targeting black individuals, followed by east and southeast Asians, indigenous individuals, and the lowest number of victims being South Asian individuals [@moreau_wang_2022]. Seeing that Canada is one of the most diverse countries in the world, welcoming 405,999 permanent immigrants in 2021 and 130,125 refugees in 2020, these statistics concerning the increase of hate crimes pose a real and visceral threat to a large proportion of Canadian residents [@government_of_canada_2022, @macrotrends].

@@

We begin our paper with a discussion of the data source, the methodologies employed in the original paper and a review of the variables used for our reproduction. We will then conduct a reproduction of their results to better improve upon the accessibility of their findings. Our paper will conclude with a discussion of our findings where we conduct a case study to apply our findings to Alberta, Canada's only Province with a greater population of males, a discussion of ethical biases, limitations and a push for future research.

@@

(1) Non-immigrant German men who live in municipalities with excess male populations are more likely to perceive refugees as threats.

(2) Non-immigrant German men who perceive mate competition are more likely to support violence as the only means to gain the attention of German politicians.

@@

## Future Research
As suggested in their original paper, Dancygier, Egami, Jamal, and Rischke call for future research to investigate how their findings apply to less ethnically distinct groups, with less aggressive media attention and under non-heteronormative roles (cite paper). They further call for tests in ethnonational countries and in regions where females overpopulate males to see if their findings apply to women (cite paper). As Global migration and refuge continue to increase, we anticipate that this field of study will become increasingly significant. It is thus crucial to expand on their findings to assess how they apply in varying nations. This is in hopes to create policy changes and account for preventative measures to avoid increased anti-refugee sentiments and hate crimes caused by sex-driven competition. We further hope for this field of research to be applied under less heteronormative circumstances and work to account for queer-identifying individuals.
